On the application of microwave acoustic resonant viral inactivation \thanks{I would be delighted to include any criticisms or comments anyone may have; preferably leave them on the GitHub issues page, or email therobotist@gmail.com, @0xDBFB7 on Twitter, or irc.0xDBFB7.com:6667 \#covid.}

### 2020-06-24 documents/paper.tex
YAAAAAAAAAY

Even with judicious use of phased-arrays, power-combining, etc, each transistor can only reasonably sterilize approx. $ 1 \text{ m}^3 $.

@@

A minimally-invasive bronchoscopic technique may be effective when mounted on a modified brochoscope and periodically inserted into the main bronchus, a la [Yuan 2019].

@@

Many weather radar systems operate in these X-band frequency ranges.

It is relatively easy to produce megawatts of power at these frequency ranges using Klystrons. Airborne phased-arrays.

@@

With large feedback-loop structures, such as PiN switched lines, proximity effects from nearby flesh would detune the oscillator to a s

@@

@@

The frequency impedance of an antenna can be determined by applying a gaussian pulse to a hard voltage source on the feedline, running the simulation until the transients have all died out while logging the voltage and current at each timestep, and then taking the fourier transform of the voltage and current. This is much faster and

However, a similar mismatch to the SPICE exists for FFT methods, but in the other direction.  The courant limit often demands fine timesteps, but since each FFT bin is $ f_bin = n_bin * (1 / (N_simulation * dt)) $ , the majority of the FFT bins exist into the hundreds or thousands of GHz, leaving no resolution in the low-frequency domain of interest unless $N_simulation$ is extremely large - even if all the transients in the simulation have died down, you still have to keep the sim running to make the FFT happy!

@@

But, in a personally staggering turn of events which will presumably be familiar to statisticans and preposterous to everyone else, a far simpler method is to {\it discard} 95\% of the data! Re-sampling some fraction of the current

An equally simple method that seemed to produce better results in our case is to {\it pad }

@@

Though uneven dt FFTs exist, the time step can be constant here .

A step impulse (1 first timestep, 0 otherwise) can also be used, though the performance is almost unusable worse.

>>>>

Even with judicious use of phased-arrays, spatial power-combining, etc, each transistor can only reasonably sterilize approx. $ 1 \text{ m}^3 $.

@@

A minimally-invasive bronchoscopic technique may be effective when mounted on a modified brochoscope and periodically inserted into the main bronchus, as demonstrated by [Yuan 2019].

@@

Many systems operate in these X-band frequency ranges; and precision

It is relatively easy to produce megawatts of power at these frequency ranges using Klystrons.

Existing marine, weather, and aviation radar systems often use the X-band; depending on the focusing power

@@

With large feedback-loop structures, such as long PiN-switched phasing lines, proximity effects from nearby flesh would detune the oscillator significantly.

@@

Thanks to P.B and H.P. for tolerating ramblings and M. for the hug.

@@

Originally tried

The frequency impedance of an antenna can be determined by:

\begin{itemize}
  \item Applying a gaussian pulse to a hard voltage source on the feedline
  \item Running the simulation until the transients have all died out below some threshold, while logging the source voltage and current at each timestep

  \item Taking the fourier transform of the (real) excitation voltage and current (producing a complex result, mind you)
  \item Taking the ratio of the two complex spectra.
\end{itemize}

However, a similar mismatch to the SPICE exists for fourier methods, but in the other direction.  The courant limit often demands fine timesteps, but since each FFT bin is $ f_{bin} = n_{bin} / (N_{simulation} \ dt) $ , the majority of the FFT bins exist into the hundreds or thousands of GHz, leaving no resolution in the low-frequency domain of interest unless $N_{simulation}$ is extremely large - even if all the transients in the simulation have died down, you still have to keep the sim running to make the FFT happy!

@@

But, in a personally staggering turn of events which will presumably be familiar to statisticans and preposterous to everyone else, a far simpler method is to {\it discard} 95\% of the data, by down-sampling to 1/10th.

An equally simple method that seemed to produce better results in our case is to pad the voltage and current samples to the correct length.

It's so thumpingly unintuitive to me that adding 50,000 zeros to a 5000 value dataset can improve the resolution of a measurement by 300-fold.

@@

Though uneven dt FFTs exist, the time step can be made constant at the courant limit.

A step impulse (1 first timestep, 0 otherwise) has been used in some works, though in our case the performance was horrid.

A method of moments solver like NEC-2 may have provided faster results; but handling of multiple dielectrics does not seem to be simple.

This technique is equivalent to that used in electrochemistry for fourier impedance - except they seem to usually use a known impedance source rather than a hard source.

The duration of the simulation is very important. When they say

Many equations in papers on the FDTD method are supplied without explicit scaling factors. For instance, for use with flaport/fdtd the H-field to current line integral in [] requires scaling by $\mu_0  (dx/dt)$, where $\mu_0$ is the vacuum magnetic permittivity, dx the cell size, and dt the timestep - despite the equation already possessing a deceptive set of $dx$-es.

Naturally, if one is competent, this discrepancy will be immediately obvious. Those not dimensionally-intuitive, such as myself, find it useful to run a test using a unit-aware calculator such as {\it sharkdp/insect}.
